

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Bradley Grose} \\ \vspace{1pt}
    \small (203) 733-0719 $|$ \href{mailto:x@x.com}{\underline{bradley@grose.net}} $|$ 
    \href{https://linkedin.com/in/...}{\underline{linkedin.com/in/bradley-grose/}} $|$
    \href{https://github.com/...}{\underline{github.com/bgrose}}
\end{center}

\section{}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of South Carolina}{Columbia, SC}
      {Bachelor of Science in Computer Science, Minor in Data Science, GPA 4.000}{Aug. 2019 -- May 2023}
  \resumeSubHeadingListEnd

\section{}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Data Science/IT Intern}{May 2021 -- Present}
      {INVISTA - Koch Industries}{Lugoff, SC}
      \resumeItemListStart
        \resumeItem{Analyzed data using a machine learning algorithm and neural network I designed to better understand improvements to chemical plants using AWS SageMaker and Python/Jupyter Notebooks.}
        \resumeItem{Automated various tasks around fiber production areas using autonomous ground vehicles to eliminate the need for manual labor, saving an estimated \$160k annually.}
        \resumeItem{Developed XR and AR functionality using Matterport and Unity to better connect factory workers to the technology and machinery through training, saving an estimated \$250k.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Tactical Software Engineering Intern}{May 2020 -- Aug. 2020}
      {General Dynamics - Electric Boat}{Groton, CT}
      \resumeItemListStart
        \resumeItem{Collaborated on an agile development team to design a new thin line towed array sonar system for Virginia Class submarines.}
        \resumeItem{Programmed with C++ and Java/JavaFX to develop and improve functions and unit tests for final product to be delivered to Department of Defense.}
        \resumeItem{Developed an output stream with Java and C++ for the sailor as well as engineers to have a log tailored to them in case of errors on the submarine.}
        
    \resumeItemListEnd

    \resumeSubheading
      {Undergraduate Teaching Assistant}{Aug. 2020 -- June 2021}
      {University of South Carolina - Dr. Jeremiah Shephard CSCE 145/146}{Columbia, SC}
      \resumeItemListStart
        \resumeItem{Educated students using Java as an introduction to programming, object oriented
        programming, and data structure.}
        \resumeItem{Using office hours and communications with students, I was able to provide feedback with debugging and coding structures to help students develop successful labs and homework}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{}

%-----------Leadership & Organizational Experience-----------
\section{Leadership \& Organizational Experience}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Theta Tau Professional Engineering Fraternity} $|$ \emph{Professional Development Chair}}{Sep. 2019 -- Present}
          \resumeItemListStart
            \resumeItem{Organized and executed professional development events to benefit all members of the fraternity}
            \resumeItem{Designed an improved alumni network database for networking opportunities over many different career fields}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Tau Beta Pi Engineering Honor Society} }{Nov 2020 -- Present}
          \resumeItemListStart
            \resumeItem{Honor Society for Engineering and Computing Majors in the College of Engineering and Computing at USC.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


\section{}
%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills \& Awards}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, C/C++, R, JavaScript, Bash} \\
     \textbf{Developer Tools}{: Git, AWS S3/SageMaker, VS Code, IntelliJ, Eclipse, PowerBI, OSIsoft, JIRA} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib, TensorFlowm Keras, SkLearn, Seaborn} \\
     \textbf{Awards}{: Presidents List, Deans List (All Semesters), Eagle Scout}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
